Exploring the World Inside US Prisons for Safety, Health, and Isolation

### 2024-02-13 outputs/paper/paper.qmd
update

```{r}
#| include: false
#| warning: false
#| message: false
install.packages("haven")  # Install the haven package
install.packages("openxlsx")
install.packages("knitr")
install.packages("kableExtra")
library(kableExtra)
library(openxlsx)
library(haven)  # Load the haven package
library(tidyverse)
library(palmerpenguins)
library(dplyr)
library(knitr)
```

@@

library(openxlsx)

# Read the Excel file
x0 <- read.xlsx(file_path, sheet = 1)
par(mfrow=c(3,1))
par(fig=c(.05,.95, 2/3-.02, 1))
plot(x0$Year, x0$Prison.Rate.per.100k, type="l", col="blue",
     xlim=c(1920, 2020), ylim=c(0, 800),
     xlab="", ylab="Incarceration Rate (per 100,000)", lty=1, lwd=2)
title(" US Incarceration, 1925-2018")
lines(x0$Year, x0$TotalRate, lty=2, col="red", lwd=2)
legend(1925, 770, c("Prison and jail","Prison only"), lwd=2,
       lty=c(2,1), col=c("red","blue"), bty="n")
abline(h=seq(0, 800, 200), v=seq(1920,2020,20), lty=3, col="gray")

```
```{r fig.height=6, fig.width=6 }
#| label: fig-men
#| fig-cap: Men’s cumulative imprisonment risk, by cohort
#| echo: false
#| warning: false
#| message: false

library(openxlsx)

@@

data <- read.xlsx(file_path, sheet = 3)
data <- data %>%
  mutate(
    race = case_when(
      race == "W" ~ "White",
      race == "B" ~ "Black",
      TRUE ~ race
    ),
    cohort = case_when(
      cohort == "45-49" ~ "Born 1945-1949",
      cohort == "75-79" ~ "Born 1975-1979",
      TRUE ~ cohort
    )
  )
ggplot(data, aes(x = race, y = risk, fill = education)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~cohort) +
  labs(
       x = "Race",
       y = "Risk",
       fill = "Education") +
  theme_minimal()

@@

data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))

data <- data[order(-data$prison_population_rate), ]

# Create the bar plot
plot <- ggplot(data, aes(x =prison_population_rate, y = country)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
  labs(x = "Prison Population Rate", y = "country")  # Add axis labels

@@

x <- data_1[data_1$admit==1,]

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
install.packages("haven")  # Install the haven package
install.packages("openxlsx")
install.packages("knitr")
install.packages("kableExtra")
install.packages("readxl")
library(readxl)
library(kableExtra)
library(openxlsx)
library(haven)  
library(tidyverse)
library(palmerpenguins)
library(dplyr)
library(knitr)
```

@@

file_path <- here::here("inputs/data/mass incarceration.xlsx")
x0 <- read.xlsx(file_path, sheet = 1)

par(mfrow=c(3,1))
par(fig=c(.05,.95, 2/3-.02, 1))
plot(x0$Year, x0$Prison.Rate.per.100k, type="l", col="blue",
     xlim=c(1920, 2020), ylim=c(0, 800),
     xlab="", ylab="Incarceration Rate (per 100,000)", lty=1, lwd=2)
lines(x0$Year, x0$TotalRate, lty=2, col="red", lwd=2)
legend(1925, 770, c("Prison and jail","Prison only"), lwd=2,
       lty=c(2,1), col=c("red","blue"), bty="n")
abline(h=seq(0, 800, 200), v=seq(1920,2020,20), lty=3, col="gray")

```{r fig.height=6, fig.width=6 }
#| label: fig-men
#| fig-cap: Men’s cumulative imprisonment risk, by cohort
#| echo: false
#| warning: false
#| message: false

@@

men_data <- read.xlsx(file_path, sheet = 3)
men_data <- men_data %>%
  mutate(
    race = case_when(
      race == "W" ~ "White",
      race == "B" ~ "Black",
      TRUE ~ race
    ),
    cohort = case_when(
      cohort == "45-49" ~ "Born 1945-1949",
      cohort == "75-79" ~ "Born 1975-1979",
      TRUE ~ cohort
    )
  )
ggplot(men_data, aes(x = race, y = risk, fill = education)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~cohort) +
  labs(
       x = "Race",
       y = "Risk",
       fill = "Education") +
  theme_minimal()

@@

c_data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))

c_data <- data[order(-data$prison_population_rate), ]

# Create the bar plot
plot <- ggplot(c_data, aes(x =prison_population_rate, y = country)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
  labs(x = "Prison Population Rate", y = "country")  # Add axis labels

@@

data_3 <- read_dta('../../inputs/data/spi86to16.dta')

x <- data_3[data_3$admit==1,]
